---
title: "rMSIfragment Figures"
output: html_notebook
---

This R Markdown was used to generate the figures of the publication of rMSIfragment. It serves two purposes:
(1) Transparency and replicability of the figures
(2) Demonstration of an several applications of rMSIfragment (for a more detailed demonstration explore demo.Rmd)

### 0. Load data
```{r}

```
### Figure 1. Manual Validation
```{r}

```
### Figure 2. Target Decoy Validation
```{r}

```
### Figure 3. METASPACE Validation
```{r}

```
### Figure 4. Example application
```{r}

```

```{r}
pks<-rMSIproc::LoadPeakMatrix("/home/gbaquer/msidata/1. In-source Fragmentation/1.5. Validation Datasets/2. Nevus articulo fragmentación/pks_neg.zip")
metrics<-c("lipid_occurences","correlation","lipid_occurences*(correlation+1)","parental_percentage","fragment_percentage","km_correlation","km_correlation_old")

res1<-target_decoy_validation(pks,db_t,db_d,mode="neg",tol=5)
res2<-target_decoy_validation(pks,db_t,db_d,mode="neg",tol=5,d_type = F)

plot_figure1(res1,metrics,label="_NEG_D1_N")
plot_figure1(upsample(res1),metrics,label="_NEG_D1_U")
plot_figure1(downsample(res1),metrics,label="_NEG_D1_D")

plot_figure1(res2,metrics,label="_NEG_D2_N")
plot_figure1(upsample(res2),metrics,label="_NEG_D2_U")
plot_figure1(downsample(res2),metrics,label="_NEG_D2_D")

res<-annotate(pks,db_t,20,"neg")
res5ppm<-annotate(pks,db_t,5,"neg")
plot_figure3(pks,res5ppm,744.558,3,label="_5ppm_top3")

plot_figure2(res5ppm,load_gt(),"adduct_score",label="_adduct_score")
plot_figure2_topN(res,load_gt())
#Downsample T
plot_roc(res1[c(sample(which(res$db=="T"),sum(res$db=="D")),which(res$db=="D")),],c("lipid_occurences","correlation","lipid_occurences*correlation","lipid_occurences*(correlation+1)","parental_percentage","fragment_percentage","km_correlation","km_correlation_old"))
plot_roc(res2[c(sample(which(res$db=="T"),sum(res$db=="D")),which(res$db=="D")),],c("lipid_occurences","correlation","lipid_occurences*correlation","lipid_occurences*(correlation+1)","parental_percentage","fragment_percentage","km_correlation","km_correlation_old"))

#Upsample D
plot_roc(tmp,c("lipid_occurences","correlation","lipid_occurences*correlation","lipid_occurences*(correlation+1)*(fragment_percentage+1)","parental_percentage","fragment_percentage","km_correlation","km_correlation_old"))

tmp2<-res2
new_rows2<-nrow(tmp2)+(1:(with(res2,sum(db=="T")-sum(db=="D"))))
tmp[new_rows2,]<-NA
tmp2[new_rows2,"db"]<-"D"
tmp2[new_rows2,c("lipid_occurences","correlation","km_correlation","km_correlation_old","fragment_percentage","parental_percentage")]<-0
tmp2[new_rows2,"lipid_occurences"]<-1
plot_roc(tmp2,c("lipid_occurences","correlation","lipid_occurences*correlation","lipid_occurences*(correlation+1)*(fragment_percentage+1)","parental_percentage","fragment_percentage","km_correlation","km_correlation_old"))

#Smaller DB
table_neg<-load_gt()
is<-with(db_t,paste(lipid,c,delta))%in%unique(with(table_neg,paste(lipid,c,delta)))
res<-target_decoy_validation(pks,db_t[is,],db_d[is,],mode="neg",tol=5)
plot_roc(res,c("lipid_occurences","correlation","lipid_occurences*correlation"))


man_val<-manual_validation(subset(res1,db=="T"),load_gt())
```

