---
title: "rMSIfragment Figures"
output: html_notebook
---

This R Markdown was used to generate the figures of the publication of rMSIfragment (DOI). It serves two purposes:
(1) Transparency and reproducibility of results
(2) Demonstration of the main applications of rMSIfragment (for a more detailed demonstration explore demo.Rmd)

### Load dependencies
```{r}
library(rMSI)
library(rMSIproc)
library(rMSIfragment)

library(ggplot2)
library(viridisLite)
```

### 0.1. Load data
```{r,echo=FALSE,message=FALSE,warning=FALSE}
#Load adduct and in-source fragment lipid pathways
data(d)
rMSIfragment:::updateEnv(d)

#Load libraries
load("E:/in-source fragmentation/DATA/target_decoy_db_new.RData")

#Load experimental data
pks_neg<-rMSIproc::LoadPeakMatrix("E:/in-source fragmentation/DATA/pks_neg.zip")
pks_pos<-rMSIproc::LoadPeakMatrix("E:/in-source fragmentation/DATA/pks_pos.zip")

#Load metrics to compare
#metrics<-c("lipid_occurences","correlation","lipid_occurences*(correlation+1)","parental_percentage","fragment_percentage","km_correlation","km_correlation_old")
metrics<-c("lipid_occurences","correlation","S","parental_percentage","fragment_percentage","km_correlation","km_correlation_old")


#Load Ground Truths
gt_neg<-rMSIfragment:::load_gt("E:/in-source fragmentation/DATA/gt_neg.csv")
gt_pos<-rMSIfragment:::load_gt("E:/in-source fragmentation/DATA/gt_pos.csv")

```
### 0.2. Annotate in-source fragments and adducts
```{r,,echo=FALSE,message=FALSE,warning=FALSE}
rMSIfragment:::updateEnv(d)
# res.neg.5ppm.td1<-rMSIfragment:::target_decoy_validation(pks_neg,db_t,db_d,mode="neg",tol=5)
# res.neg.5ppm.td2<-rMSIfragment:::target_decoy_validation(pks_neg,db_t,db_d,mode="neg",tol=5,d_type = F)
# res.neg.20ppm.td1<-rMSIfragment:::target_decoy_validation(pks_neg,db_t,db_d,mode="neg",tol=20)
# res.neg.20ppm.td2<-rMSIfragment:::target_decoy_validation(pks_neg,db_t,db_d,mode="neg",tol=20,d_type = F)
# 
res.pos.5ppm.td1<-rMSIfragment:::target_decoy_validation(pks_pos,db_t,db_d,mode="pos",tol=5)
res.pos.5ppm.td2<-rMSIfragment:::target_decoy_validation(pks_pos,db_t,db_d,mode="pos",tol=5,d_type = F)
# res.pos.20ppm.td1<-rMSIfragment:::target_decoy_validation(pks_pos,db_t,db_d,mode="pos",tol=20)
# res.pos.20ppm.td2<-rMSIfragment:::target_decoy_validation(pks_pos,db_t,db_d,mode="pos",tol=20,d_type = F)

# res.neg.20ppm<-rMSIfragment::annotate(pks_neg,db_t,20,"neg")
# res.neg.5ppm<-rMSIfragment::annotate(pks_neg,db_t,5,"neg")
res.pos.20ppm<-rMSIfragment::annotate(pks_pos,db_t,20,"pos")
res.pos.5ppm<-rMSIfragment::annotate(pks_pos,db_t,5,"pos")
```

### Figure 1. Manual Validation (Negative mode 5 ppm)
```{r, fig.width=15}
rMSIfragment:::plot_figure1(res.neg.5ppm.td1,metrics[1:3],label="_NEG_D1_N")
rMSIfragment:::plot_figure2(pks_neg,res.neg.5ppm,gt_neg,"S",steps = 1000,label="_adduct_score")
rMSIfragment:::plot_figure3(pks_neg,res.neg.5ppm,744.558,3,label="_5ppm_top3")

rMSIfragment:::plot_figure1(res.neg.5ppm.td2,metrics[1:3],label="_NEG_D1_N")
rMSIfragment:::plot_figure2(pks_neg,res.neg.20ppm,gt_neg,"S",steps = 1000,label="_adduct_score")
rMSIfragment:::plot_figure3(pks_neg,res.neg.20ppm,744.558,3,label="_5ppm_top3")
```
### Check separation between parental vs fragment
```{r}
#Compute parental
tmp<-rMSIfragment:::manual_validation(res.neg.20ppm,gt_neg)
t<-tmp$table
a<-subset(d$adducts,mode=="neg")$name
t$parental<-t$adduct%in%a
subset(t,!match&HPLC_adduct!="_")

#Quantify score for HPLC
tmp$res$match_HPLC_adduct
i<-tmp$res$match_HPLC_adduct!=""
pval<-mean(sapply(1:100,function(j)wilcox.test(sample(tmp$res$S[!i],sum(i)), tmp$res$S[i], alternative = "two.sided")$p.value))

```
### PR curve
```{r}
#roc<-td_roc(tmp$res$S,i,mz_i)
#auc<-mean(sapply(1:500,function(j)PRROC::pr.curve(scores.class1 = sample(tmp$res$S[!i],sum(i)),scores.class0=tmp$res$S[i],curve=T)$auc.integral))
pr<-PRROC::pr.curve(scores.class1 = tmp$res$S[i],scores.class0=tmp$res$S[!i],curve=T)
  df<-data.frame(x=pr$curve[,1],y=pr$curve[,2])

  pb<-ggplot(df,aes(x,y))+geom_line(size=2)+
    xlab("Recall")+ylab("Precision")+
    theme_bw()+theme(legend.justification = c(1, 0), legend.position = c(1, 0),legend.background=element_rect(size=0.2,colour=1),panel.border = element_rect(colour = "black", fill=NA), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), plot.title = element_text(hjust = 0),text=element_text(size=20)) +
    ggtitle("B")#+
    #scale_color_discrete(name = "Score", breaks = names,labels = paste(names," (",round(pr$auc.integral,2)," AUC)",sep = ""))
pb
pr$auc.integral


rcFinal$curve<-
rc<-PRROC::roc.curve(scores.class0 = tmp$res$S[i],scores.class1=sample(tmp$res$S[!i],sum(i)),curve=T)
  df<-data.frame(x=rc$curve[,1],y=rc$curve[,2])

  pc<-ggplot(df,aes(x,y))+geom_line(size=2)+
    xlab("False Positive Rate")+ylab("Sensitivity")+
    theme_bw()+theme(legend.justification = c(1, 0), legend.position = c(1, 0),legend.background=element_rect(size=0.2,colour=1),panel.border = element_rect(colour = "black", fill=NA), panel.grid.major = element_blank(),
                     panel.grid.minor = element_blank(), plot.title = element_text(hjust = 0),text=element_text(size=20)) +
    ggtitle("c")#+
    #scale_color_discrete(name = "Score", breaks = names,labels = paste(names," (",round(pr$auc.integral,2)," AUC)",sep = ""))
pc
rc$auc
```
```{r}
###
rc2<-lapply(1:1000,function(j)PRROC::roc.curve(scores.class0 = tmp$res$S[i],scores.class1=sample(tmp$res$S[!i],sum(i)),curve=T))
df<-data.frame(x=unlist(lapply(rc2,function(x)x$curve[,1])),y=unlist(lapply(rc2,function(x)x$curve[,2])),id=rep(1:length(rc2),times=sapply(rc2,function(x)length(x$curve[,1]))))
ggplot(df, aes(x = x, y = y)) +
  geom_line(aes(group = id), alpha = 0.5) +
  geom_smooth(size = 0.8, se = F, span = 0.2)
```


```{r, fig.width=15}
#rMSIfragment:::plot_figure1(res.pos.5ppm.td1,metrics[1:3],label="_NEG_D1_N")
rMSIfragment:::plot_figure2(pks_pos,res.pos.5ppm,gt_pos,"S",steps = 1000,label="_adduct_score")
#rMSIfragment:::plot_figure3(pks_pos,res.pos.5ppm,744.558,3,label="_5ppm_top3")

#rMSIfragment:::plot_figure1(res.pos.5ppm.td2,metrics[1:3],label="_NEG_D1_N")
rMSIfragment:::plot_figure2(pks_pos,res.pos.20ppm,gt_pos,"S",steps = 1000,label="_adduct_score")
#rMSIfragment:::plot_figure3(pks_pos,res.pos.20ppm,744.558,3,label="_5ppm_top3")
```
### Figure 1. Manual Validation (Negative mode 20 ppm)
```{r, fig.width=15}
rMSIfragment:::plot_figure1(res1,metrics,label="_NEG_D1_N")
rMSIfragment:::plot_figure2(pks_neg,res,gt_neg,"adduct_score",label="_adduct_score")
rMSIfragment:::plot_figure3(pks_neg,res,744.558,3,label="_5ppm_top3")
```

### Figure 2. Target Decoy Validation
```{r}

```
### Figure 3. METASPACE Validation (They use 3ppm tolerance)
```{r}
files=list.files(path = "E:/in-source fragmentation/METASPACE/",pattern = "*.zip", full.names = TRUE,recursive = T)
pks_MS<-lapply(files,rMSIproc::LoadPeakMatrix)
csvfiles=gsub(".zip",".csv",files)
ann_MS<-lapply(csvfiles,function(x)read.csv(x,skip=2))
df<-data.frame(name=basename(files))
df$mode<-sapply(strsplit(basename(files),"_"),function(x)tolower(x[1]))
df$matrix<-sapply(strsplit(basename(files),"_"),function(x)tolower(x[2]))
df$specimen<-sapply(strsplit(basename(files),"_"),function(x)tolower(x[3]))
df$tissue<-sapply(strsplit(basename(files),"_"),function(x)tolower(x[4]))
df$analyzer<-sapply(strsplit(basename(files),"_"),function(x)tolower(x[4]))
df$mz.mean<-sapply(pks_MS,function(x)mean(x$mass))
df$mz.max<-sapply(pks_MS,function(x)max(x$mass))
df$mz.min<-sapply(pks_MS,function(x)min(x$mass))
```
### Annotate with rMSIfragment
```{r}
res_MS<-lapply(seq_along(pks_MS),function(i)rMSIfragment::annotate(pks_MS[[i]],new,3,df$mode[i]))
```

```{r}
rbind(sapply(res_MS,nrow),sapply(ann_MS,nrow),sapply(pks_MS,function(x)min(x$mass)),sapply(pks_MS,function(x)max(x$mass)))
```
### Compare the results
```{r}
i<-10



comp<-lapply(seq_along(pks_MS),function(i)compareToMetaspace(res_MS[[i]],ann_MS[[i]],pks_MS[[i]]))
```

```{r}
df$covered<-sapply(comp,function(x)x$covered)
df$matching<-sapply(comp,function(x)x$matching)
df$overlappedWithFragments<-sapply(comp,function(x)x$overlappedWithFragments)
df$compoundsWithFragments<-sapply(comp,function(x)x$compoundsWithFragments)
ggplot(df,aes(x=matching,y=covered,label=1:16))+geom_point()+geom_text(hjust=0,vjust=0)
```


### Figure 4. Example application
```{r}
pks_MUN<-rMSIproc::LoadPeakMatrix("E:/in-source fragmentation/MUNSTER/Munster_Au_Res_140k_10um.zip")
```
```{r}
rMSIproc::plotPeakImage(pks_MUN,column=1000)
```
### Updating the databases
```{r}
new<-rMSIfragment:::load_lipidMAPS("E:/in-source fragmentation/DATA/db/LMSD.sdf")
old<-rMSIfragment:::load_lipidMAPS("E:/in-source fragmentation/DATA/db/LMSDold.sdf")
tmp<-rMSIfragment:::load_decoy_non_animal(NA,"E:/in-source fragmentation/DATA/chebi/")

plot(density(tmp$exactmass))
lines(density(db_t$exactmass))
tmp2<-rMSIfragment:::adjust_db_densities(db_t,tmp)
lines(density(tmp2$exactmass))

db_d<-tmp2

save(list=c("db_t","db_d"),file="E:/in-source fragmentation/DATA/target_decoy_db_new.RData")
```

### Move to figure generation new Use either 4, 6 or 8
```{r}
lapply(pks_MS,function(x)rMSIproc::plotPeakImage(x,column=900))
```
### Using 4
```{r}
## Look for interesting annotations
them<-ann_MS[[4]]
us<-res_MS[[4]]
a1<-ours
a2<-subset(a1,fragmentation=="")
a3<-subset(a1,fragmentation!="")
b<-metaspace
b$mz_i<-sapply(b$mz,function(x) which.min(abs(pks$mass-x)))
matching<-(paste(us$formula,us$adduct)%in%paste(them$formula,them$adduct))&(us$fragmentation=="")

matched_us<-us[matching,]
matched_us<-matched_us[order(matched_us$S,decreasing = T),]


## Interesting experimental masses

772.5864
744.5553
887.5661
788.5452

```


```{r,fig.width=10,fig.height=10}
rMSIfragment:::plot_figure3(pks_MS[[4]],res_MS[[4]],772.5864,3,label="_5ppm_top3")
rMSIfragment:::plot_figure3(pks_MS[[4]],res_MS[[4]],744.5553,3,label="_5ppm_top3")
rMSIfragment:::plot_figure3(pks_MS[[4]],res_MS[[4]],887.5661,3,label="_5ppm_top3")
rMSIfragment:::plot_figure3(pks_MS[[4]],res_MS[[4]],788.5452,3,label="_5ppm_top3")
```
```{r}
them[which.min(abs(them$mz-887.57)),]
them[which.min(abs(them$mz-836.53)),]
them[which.min(abs(them$mz-749.51)),]
```


### Reprocess all datasets
```{r}
files_imzML=list.files(path = "E:/in-source fragmentation/METASPACE/new3/",pattern = "*.imzML", full.names = TRUE,recursive = T)
files_zip=gsub("*.imzML",".zip",files_imzML)

for(i in seq_along(files_imzML)){
  tmp<-rMSIworkflows:::loadBinnedCentroidData(files_imzML[i],3)
  rMSIproc::StorePeakMatrix(files_zip[i],tmp)
}
```

### Focus on dataset 3
```{r}

tmp<-rMSIworkflows:::loadBinnedCentroidData("E:/in-source fragmentation/METASPACE/imzML/NEG_DAN_MOUSE_MUSCLE_ORBITRAP.imzML",3)

```
```{r,echo=FALSE,message=FALSE,warning=FALSE}
i=3
tol=50
tmp2<-rMSIfragment::annotate(tmp,new,3,df$mode[i])

ann_MS[[3]]$formula%in%new$formula

exp_mz<-pks_MS[[i]]$mass
a<-d$adducts$mass[d$adducts$name=="M-H"]
db_mz<-new$exactmass
target<-db_mz+a

#Generate matches
min<-target-target*tol*10^-6
max<-target+target*tol*10^-6

match<-sapply(exp_mz,function(x)x<max&x>min)


apply(match,2,any)
```
```{r,echo=FALSE,message=FALSE,warning=FALSE}
tmp4<-rMSIfragment::annotate(tmp,new,10,df$mode[i])
```
```{r,echo=FALSE,message=FALSE,warning=FALSE}
tmp5<-rMSIfragment::annotate(tmp,db_t,3,df$mode[3])
tmp6<-rMSIfragment::annotate(tmp,db_t,10,df$mode[3])
```

```{r}
comp<-list()
comp[[1]]<-rMSIfragment:::compareToMetaspace(tmp2,ann_MS[[3]],tmp)
comp[[2]]<-rMSIfragment:::compareToMetaspace(tmp4,ann_MS[[3]],tmp)
comp[[3]]<-rMSIfragment:::compareToMetaspace(tmp2,subset(ann_MS[[3]],fdr<0.2),tmp)
comp[[4]]<-rMSIfragment:::compareToMetaspace(tmp4,subset(ann_MS[[3]],fdr<0.2),tmp)

comp[[5]]<-rMSIfragment:::compareToMetaspace(tmp5,ann_MS[[3]],tmp)
comp[[6]]<-rMSIfragment:::compareToMetaspace(tmp6,ann_MS[[3]],tmp)
comp[[7]]<-rMSIfragment:::compareToMetaspace(tmp5,subset(ann_MS[[3]],fdr<0.2),tmp)
comp[[8]]<-rMSIfragment:::compareToMetaspace(tmp6,subset(ann_MS[[3]],fdr<0.2),tmp)

rbind(sapply(comp,function(x)x$matching),sapply(comp,function(x)x$overlappedWithFragments),sapply(comp,function(x)x$compoundsWithFragments))

```



```{r}
pks<-rMSIproc::LoadPeakMatrix("/home/gbaquer/msidata/1. In-source Fragmentation/1.5. Validation Datasets/2. Nevus articulo fragmentación/pks_neg.zip")
metrics<-c("lipid_occurences","correlation","lipid_occurences*(correlation+1)","parental_percentage","fragment_percentage","km_correlation","km_correlation_old")

res1<-target_decoy_validation(pks,db_t,db_d,mode="neg",tol=5)
res2<-target_decoy_validation(pks,db_t,db_d,mode="neg",tol=5,d_type = F)

plot_figure1(res1,metrics,label="_NEG_D1_N")
plot_figure1(upsample(res1),metrics,label="_NEG_D1_U")
plot_figure1(downsample(res1),metrics,label="_NEG_D1_D")

plot_figure1(res2,metrics,label="_NEG_D2_N")
plot_figure1(upsample(res2),metrics,label="_NEG_D2_U")
plot_figure1(downsample(res2),metrics,label="_NEG_D2_D")

res<-annotate(pks,db_t,20,"neg")
res5ppm<-annotate(pks,db_t,5,"neg")
plot_figure3(pks,res5ppm,744.558,3,label="_5ppm_top3")

plot_figure2(res5ppm,load_gt(),"adduct_score",label="_adduct_score")
plot_figure2_topN(res,load_gt())
#Downsample T
plot_roc(res1[c(sample(which(res$db=="T"),sum(res$db=="D")),which(res$db=="D")),],c("lipid_occurences","correlation","lipid_occurences*correlation","lipid_occurences*(correlation+1)","parental_percentage","fragment_percentage","km_correlation","km_correlation_old"))
plot_roc(res2[c(sample(which(res$db=="T"),sum(res$db=="D")),which(res$db=="D")),],c("lipid_occurences","correlation","lipid_occurences*correlation","lipid_occurences*(correlation+1)","parental_percentage","fragment_percentage","km_correlation","km_correlation_old"))

#Upsample D
plot_roc(tmp,c("lipid_occurences","correlation","lipid_occurences*correlation","lipid_occurences*(correlation+1)*(fragment_percentage+1)","parental_percentage","fragment_percentage","km_correlation","km_correlation_old"))

tmp2<-res2
new_rows2<-nrow(tmp2)+(1:(with(res2,sum(db=="T")-sum(db=="D"))))
tmp[new_rows2,]<-NA
tmp2[new_rows2,"db"]<-"D"
tmp2[new_rows2,c("lipid_occurences","correlation","km_correlation","km_correlation_old","fragment_percentage","parental_percentage")]<-0
tmp2[new_rows2,"lipid_occurences"]<-1
plot_roc(tmp2,c("lipid_occurences","correlation","lipid_occurences*correlation","lipid_occurences*(correlation+1)*(fragment_percentage+1)","parental_percentage","fragment_percentage","km_correlation","km_correlation_old"))

#Smaller DB
table_neg<-load_gt()
is<-with(db_t,paste(lipid,c,delta))%in%unique(with(table_neg,paste(lipid,c,delta)))
res<-target_decoy_validation(pks,db_t[is,],db_d[is,],mode="neg",tol=5)
plot_roc(res,c("lipid_occurences","correlation","lipid_occurences*correlation"))


man_val<-manual_validation(subset(res1,db=="T"),load_gt())
```

